---
title: "Workflow: Jinxi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow: Jinxi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r workflow, eval = FALSE}
### prerequisites (64bit R)
if(Sys.getenv("R_ARCH") != "/x64") {
  stop("Spatial operations need a lot of RAM. Use of 64bit R is required. 
  
Workflow in RStudio:  
1. Go to 'Tools' (top pane)
2. Select 'Global Options' 
3. Select 'General' 
4. Under 'R Sessions' select 'Change' 
5. Select 'Use the machine`s default R version of R64 (64-bit)'
6. Close all R Studio sessions  
7. Restart R Studio"
)
} else {
  
path_list <- list(
  root_path = "C:/kwb/projects/keys/Data-Work packages",
  site = "Jinxi",
  data = "WP2_SUW_pollution_<site>",
  abimo = "<root_path>/<data>/_DataAnalysis/abimo",
  abimo_inp_shp = "<abimo>/abimo_<site>.shp",
  abimo_inp_dbf = "<abimo>/abimo_<site>.dbf",
  abimo_out = "abimo_<site>out.dbf",
  abimo_berlin = "<abimo>/abimo_2019_mitstrassen.dbf",
  abimo_scenarios = "<abimo>/scenarios/de-coupling",
  abimo_config_original = "<abimo>/config_original.xml",
  abimo_config_modified = "<abimo>/config.xml",
  abimo_exe = "<abimo>/Abimo3_2.exe",
  gis = "<root_path>/<data>/_DataAnalysis/gis",
  climate = "<root_path>/<data>/_DataAnalysis/climate",
  emissions_input = "<root_path>/<data>/_DataAnalysis/emissions/input/annual_mean_conc.csv",
  emissions_output = "<root_path>/<data>/_DataAnalysis/emissions/output"
)

paths <- kwb.utils::resolve(path_list)

# load shapefile containing subcatchments ('blockteilflächen')
abimo <- raster::shapefile(file.path(paths$gis, 'input_subareas.shp'))

# make ABIMO 'CODE' column
names(abimo@data) <- "CODE" 

# pad CODE with zeroes to match output of ABIMO
abimo@data$CODE <- urbanAnnualRunoff::padCODE(abimo@data$CODE)

# build classification model
kwb.ml::buildClassMod(
  rawdir = paths$gis,
  image = 'input_image.img',
  groundTruth = 'input_groundtruth.shp',
  groundTruthValues = list('roof' = 1, 
                           'street' = 2,
                           'pervious' = 3,
                           'shadow' = 4,
                           'water' = 5),
  spectrSigName = 'spectrSig.Rdata',
  modelName = 'rForest.Rdata',
  overlayExists = FALSE,
  nCores = parallel::detectCores() - 1,
  mtryGrd = 1:2, 
  ntreeGrd=seq(80, 150, by=10),
  nfolds = 3, 
  nodesize = 3, 
  cvrepeats = 2)

# check model performance
load(file.path(paths$gis,"rForest.Rdata"))
caret::confusionMatrix(data = model$finalModel$predicted, 
                       reference = model$trainingData$.outcome, 
                       mode = 'prec_recall')
                       
# classify image for roofs and streets
kwb.ml::predictSurfClass(rawdir = paths$gis,
                                    modelName = 'rForest.Rdata',
                                    image = 'input_image.img',
                                    predName = 'classified_image.img')

# make overlay object (list where each element is a vector of the pixel values 
# of the classified image for each subcatchment)
urbanAnnualRunoff::makeOverlay(rawdir = paths$gis,
                               rasterData = 'classified_image.img',
                               subcatchmSPobject = abimo,
                               overlayName = 'surfType')
# make ABIMO variable FLGES
abimo@data$FLGES <- urbanAnnualRunoff::makeFLGES(subcatchmSPobject = abimo)

# compute ABIMO variable PROBAU (%roof)
abimo@data$PROBAU <- urbanAnnualRunoff::makePROBAU(
  rawdir = paths$gis,
  rasterData = 'classified_image.img',
  overlayName = 'surfType',
  targetValue = 1)
  
# compute ABIMO variable STR_FLGES (m2 street area)
abimo@data$STR_FLGES <- urbanAnnualRunoff::makeSTR_FLGES(
  rawdir = paths$gis,
  subcatchmSPobject = abimo,
  mask = 'input_maskUrbanCore.shp',
  rasterData = 'classified_image.img',
  overlayName = 'surfType',
  targetValue = 2)

# compute ABIMO variable VG (% soil sealing)
abimo@data$VG <- urbanAnnualRunoff::makeVG(
  rawdir = paths$gis,
  subcatchmSPobject = abimo,
  rasterData = 'input_impervious.tif',
  targetValue = 80)

# compute annual and summer rainfall. 
# *** potential enhancement: ***
# return the multiannual average annual rainfall. care must be taken to exclude
# incomplete years from the average calculation. same for summer rainfall
precipitation <- urbanAnnualRunoff::computeABIMOclimate(
  rawdir = paths$climate,
  file_inp = sprintf('raw_climateeng_precipitation_daily_%s.txt', 
                     paths$site),
  file_out = 'precipitation.txt',
  summer_month_start = 4)
# compute annual and summer ETP. this goes manually into the ABIMO config file
  evapotranspiration <- urbanAnnualRunoff::computeABIMOclimate(
  rawdir = paths$climate,
  file_inp = sprintf('raw_climateeng_etp_daily_%s.txt', 
                     paths$site),
  file_out = 'evapotranspiration.txt',
  summer_month_start = 4)
  
### Merge complete years (i.e. 2014-2019 for Jinxi)
### mean rainfall: 1744mm
climate_data <- dplyr::inner_join(precipitation, evapotranspiration,
                                  by = "year", 
                                  suffix = c(".p", ".etp")) %>%  
  dplyr::mutate(dplyr::across(tidyselect::ends_with("p"), round))

#wet year 2320mm (2016)
#climate_data <- climate_data %>%  dplyr::filter(year == "2016")

#dry year 1407mm (2019)
#climate_data <- climate_data %>%  dplyr::filter(year == "2019")

# annual rainfall (this can be automatized by making 'computeABIMOclimate'
# return the multiannual average annual rainfall. care must be taken to exclude
# incomplete years from the average calculation)
round_mean <- function(values) {
  round(mean(values), digits  = 0)
}

### Mean precipitation value for period 2014-2019
abimo@data$REGENJA <- round_mean(climate_data$sum_annual.p)
abimo@data$REGENSO <- round_mean(climate_data$sum_summer.p)

### Mean evapotranspiration value for period 2014-2019
kwb.abimo::abimo_xml_evap(
  file_in = paths$abimo_config_original,
  file_out = paths$abimo_config_modified,
  evap_annual = round_mean(climate_data$sum_annual.etp),
  evap_summer = round_mean(climate_data$sum_summer.etp)
)

### Check modified ABIMO config.xml
kwb.utils::hsOpenWindowsExplorer(paths$abimo_config_modified)

# compute ABIMO variable PROVGU (% other impervious areas) as 
# PROVGU = VG - PROBAU, setting any negative values to 0. this
# happens for only <10% of subcatchments, and results mainly from
# differences in spatial resolution and classification differences
# between both datasets (our classified image and the global land 
# use dataset)
abimo@data$PROVGU <- ifelse((abimo@data$VG - abimo@data$PROBAU) > 0,
                            abimo@data$VG - abimo@data$PROBAU,
                            0)

# % imperviousness streets
abimo@data$VGSTRASSE <- 100

# %cover types in other imperv. areas (PROVGU)
abimo@data$BELAG1 <- 100
abimo@data$BELAG2 <- 0
abimo@data$BELAG3 <- 0
abimo@data$BELAG4 <- 0

# %cover types in street areas
abimo@data$STR_BELAG1 <- 100
abimo@data$STR_BELAG2 <- 0
abimo@data$STR_BELAG3 <- 0
abimo@data$STR_BELAG4 <- 0

# identifiers
abimo@data$BEZIRK <- 1
abimo@data$STAGEB <- 1
abimo@data$BLOCK <- 1
abimo@data$TEILBLOCK <- 1
abimo@data$NUTZUNG <- 21
abimo@data$TYP <- 21


# channelization degrees. these are set manually since there is no data
abimo@data$KANAL <- 1
abimo@data$KAN_BEB <- 100
abimo@data$KAN_VGU <- 100
abimo@data$KAN_STR <- 100

# soil field capacity and groundwater level (personal communication, Dr. Lipin Li, 
# Harbin Inst. of Technology)
abimo@data$FELD_30 <- 30
abimo@data$FELD_150 <- 30
abimo@data$FLUR <- 1.17

# select required columns and write out new shapefile

# select required columns and write out new shapefile
requiredCols <- c('CODE', 'BEZIRK', 'STAGEB', 'BLOCK', 
                  'TEILBLOCK', 'NUTZUNG', 'TYP', 'FLGES', 
                  'STR_FLGES', 'PROBAU', 'PROVGU', 'VGSTRASSE',
                  'BELAG1', 'BELAG2', 'BELAG3', 'BELAG4',
                  'STR_BELAG1', 'STR_BELAG2', 'STR_BELAG3', 'STR_BELAG4',
                  'KAN_BEB', 'KAN_VGU', 'KAN_STR',
                  'REGENJA', 'REGENSO',
                  'FELD_30', 'FELD_150', 'FLUR')
abimo@data <- kwb.utils::selectColumns(abimo@data, 
                                       columns = requiredCols)

# format numbers to 0 decimal places (avoid 'pseudo-accuracy')
#abimo@data[, 8:ncol(abimo@data)] <- round(
#  abimo@data[, 8:ncol(abimo@data)],
#  digits = 0)

# change decimal separator to comma
# (ABIMO does not run correctly otherwise) 
abimo@data <- as.data.frame(apply(X=apply(X=abimo@data,
                                         c(1, 2),
                                         FUN=as.character),
                                 c(1, 2),
                                 FUN=gsub,
                                 pattern="\\.",
                                 replacement=","),
                           stringsAsFactors = FALSE)




# write ABIMO input table
raster::shapefile(x=abimo, 
                  filename=paths$abimo_inp_shp,
                  overwrite=TRUE)


kwb.abimo::write.dbf.abimo(abimo, 
                           new_dbf = paths$abimo_inp_dbf)


# run ABIMO manually in GUI ----------------------------------------------------
abimo_out <- sprintf('abimo_%sout.dbf', paths$site)
if(!fs::file_exists(paths$abimo_exe)) {
  stop(cat(sprintf("ABIMO executale does not exist: %s
Please copy to this location", paths$abimo_exe)))
} else {
message(cat(sprintf("Run ABIMO executable manually:
1. Select input file: \"%s\"
2. Save it under: \"%s\"", 
                    abimo_inp_path, 
                    abimo_out))
)
      
kwb.utils::hsOpenWindowsExplorer(paths$abimo_exe)

# postprocessing ----------------------------------------------------------------
# post-process ABIMO output file -> join it with input shape file for 
# visualization in GIS

scenario_results_jinxi <- urbanAnnualRunoff::get_scenario_results(paths)

#usethis::use_data(scenario_results_jinxi, overwrite = TRUE)


```

## Scenario Results

Below is a summary table with the ABIMO water balance modelling results for the different `de-coupling` scenarios. 
Combining (`combi_xxx`) the different single measures, i.e. `bioretention cells` (for streets), `green roofs` (for sealed areas with buildings),  and `permeable pavements` (for sealed areas without buildings/streets)) enables to satisfy the `VRR` (volume rainfall retended) goal defined for climate zone 4, i.e `0.70 >= VRR <= 0.85`.




```{r scenario_results, eval = TRUE}
library(urbanAnnualRunoff)
DT::datatable(urbanAnnualRunoff::scenario_results_jinxi %>%  dplyr::select(!tidyselect::all_of(c("abimo_inpout", "abimo_inpout_emissions"))))
```

